---
title: "Home of Coffee"
author: "Group 10"
date: "Data Visualization"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: united
---

```{r setup, include=FALSE}
library(ggplot2)
library(flexdashboard)
## Import Needed Packages
library(flexdashboard) 
library(highcharter) 
library(plotly) 
library(viridis) 
library(tidyverse)
library(countrycode) 
library(rjson) 
library(crosstalk) 
library(DT)
library(dplyr)
library(jpeg)
library(ggmap)
library(knitr)
library(shiny)
library(leaflet)
library(kableExtra)
```

```{r eval=F}
# this part of code will not be executed

# if you can not find the library, run codes in this trunk.
install.packages(c("ggplot2", "flexdashboard", "highcharter", "plotly", "viridis", "tidyverse", "countrycode", "rjson", "crosstalk", "DT", "jpeg", "ggmap", "knitr", "shiny", "leaflet", "kableExtra", "ggthemes"))

```

```{r}
# data preprocessing

library(ggplot2)
library(tidyverse)
# library(plotly)



## Import the Data Needed in this project  
data <- read_csv("coffee.csv")

## Data preprocessing
### Rename the columns of the data
colnames(data) <- c("Country", "Region", "Min_Altitude", "Max_Altitude", "Avg_Altitude", 
                    "Year", "Owner", "Species", "Variety", "Processing_method", "Number_of_bags", "Bag_weight",
                    "Aroma_Scores", "Flavor_Scores", "Aftertaste_Scores", "Acidity_Scores", "Body_Scores", "Balance_Scores",
                    "Uniformity_Scores", "Sweetness_Scores", "Moisture_Scores", "Total_Scores", "Color")

### Remove the missing value
del1 <- which(data$Region=="nan")
data_del1 <- data[-del1,]
del2 <- which(data_del1$Owner=="nan")
data_del2 <- data_del1[-del2,]
del3 <- which(data_del2$Variety=="nan")
data_del3 <- data_del2[-del3,]
del4 <- which(data_del3$Processing_method=="nan")
data_del4 <- data_del3[-del4,]
del5 <- which(data_del4$Color=="None")
data_cleaned <- data_del4[-del5,]

### Some data here are also unreasonable, like altitude about 100000, after searching information, we know that the suitable altiitude for growing coffee is around 1000~2000, so here we need to remove those unnormal data in column 'Avg_Altitude'.
### Here I will remove all the altitude more than 5000
data_cleaned <- data_cleaned[data_cleaned$Avg_Altitude <= 5000, ]

### After removing all the missing values, there are 796 instances remaining
### Set the type of qualitative variable as "Character" for easily visualizing
data_cleaned <- data_cleaned %>%
  mutate(Country = as.character(Country), 
         Region = as.character(Region),
         Owner = as.character(Owner),
         Species = as.character(Species), 
         Variety = as.character(Variety),
         Processing_method = as.character(Processing_method),
         Color = as.character(Color))

### In order to give audience direct recommendation of coffee, here create a new column according to the total scores called rating, 1-5, 5 means the most recommended coffee]
data_cleaned <- data_cleaned %>%
  mutate(Rating = case_when(
    Total_Scores < 65 ~ 1,
    Total_Scores >= 65 & Total_Scores < 70 ~ 2,
    Total_Scores >= 70 & Total_Scores < 80 ~ 3,
    Total_Scores >= 80 & Total_Scores < 85 ~ 4,
    Total_Scores >= 85 ~ 5
  ))

# Extract column names for filtering the variables later
valnames <- c("Aroma", "Flavor", "Aftertaste", "Acidity", "Body", "Balance",
              "Uniformity", "Sweetness", "Moisture", "Total")
valvars  <- c("Aroma_Scores", "Flavor_Scores", "Aftertaste_Scores", "Acidity_Scores", "Body_Scores", "Balance_Scores","Uniformity_Scores", "Sweetness_Scores", "Moisture_Scores", "Total_Scores")
names(valvars) <- valnames

colvars <- c("Year", "Species", "Variety", "Processing_method", "Color","Rating")
colnames <- c("Year", "Species", "Variety", "Processing Methods", "Color","Rating")
names(colvars) <- colnames
# Fix the names of some of the countries in our data to match the country names 
# used by our map later on so that they'll be interpreted and displayed. 
data_cleaned <- data_cleaned %>%
  mutate(Country = fct_recode(Country, "Tanzania, United Republic Of" = "Tanzania"),
         Country = fct_recode(Country, "Papua New Guinea" = "The Independent State of Papua New Guinea"),
         Country = fct_recode(Country, "Costa Rica" = "The Republic of Costa Rica"),
         Country = fct_recode(Country, "El Salvador" = "The Republic of El Salvador"),
         Country = fct_recode(Country, "Cote d?Ivoire" = "The Republic of Cote d'ivoire"),
         Country = fct_recode(Country, "United States of America" = "United States"))

```

```{r}
library(countrycode)
# Create new column in our data for continent. Use countrycode() to extract continents from country names.
data_cleaned$continent <- countrycode(sourcevar = data_cleaned$Country,
                              origin = "country.name",
                              destination = "continent")

# Reclassify countries that have been coded as 'Americas', by countrycode(), into 'North America' and 'South America'. 
south_america <- c('Brazil', 'Panama', 'Colombia', 'Costa Rica', 'Peru')

data_cleaned$continent[data_cleaned$Country %in% south_america] <- 'South America'
data_cleaned$continent[data_cleaned$continent=='Americas'] <- 'North America'
```

# PAGE 0 {.sidebar}

Coffee Symphony: Exploring Bean Diversity and Quality Harmony

Group Member:

2030026036 Ziao FENG (Auberon)

2030026047 Beier HE (Bella)

2030026075 Wenhao LI (Viho)

2030026100 Jingxi LU (Blair)

```{r}

```

# Variety Info

## Row

### Number of Different Coffee Varieties

```{r}
library(dplyr)
library(ggplot2)
library(plotly)
variety_count <- data_cleaned %>%
  group_by(Variety) %>%
  summarise(count = n()) %>%
  mutate(count_variety = count)

# Expanded colors vector with additional colors
colors_vector <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd",
                   "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf",
                   "#aec7e8", "#ffbb78", "#00CED1", "#c5b0d5",
                   "#c49c94", "#f7b6d2", "#c7c7c7", "#dbdb8d", "#9edae5",
                   "#add8e6", "#90ee90", "#ffb6c1", "#ffffe0", "#dda0dd",
                   "#afeeee", "#f0e68c", "#f08080", "#4682b4")  # Add more colors here

# Creating a bar plot and flipping coordinates to mimic a funnel chart
gg <- ggplot(variety_count, aes(x = reorder(Variety, count_variety), y = count_variety, fill = Variety)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  scale_fill_manual(values = colors_vector) +
  labs(title = "Number of Different Coffee Varieties",
       x = "Variety",
       y = "Count") +
  theme_minimal()

# Convert ggplot to an interactive plot using plotly

ggplotly(gg, tooltip = c("x", "y", "fill"))
```

## Row

### Coffee Output by Year and Variety

```{r}
library(dplyr)
library(ggplot2)
library(plotly)


# Define the color list
color_list <- c(
  "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd",
  "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf",
  "#1b9e77", "#d95f02", "#7570b3", "#e7298a", "#66a61e",
  "#e6ab02", "#a6761d", "#666666", "#a6cee3", "#1f78b4",
  "#b2df8a", "#33a02c", "#fb9a99", "#fdbf6f", "#ff7f00",
  "#cab2d6", "#6a3d9a"
)


gg <- ggplot(data_cleaned, aes(x = Year, y = Number_of_bags, fill = Variety)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_manual(values = color_list) +
  labs(title = "Coffee Output by Year and Variety",
       subtitle = "2011 - 2018",
       x = "Year",
       y = "Amount of Bags") +
  theme_minimal()

ggplotly(gg, tooltip = c("x", "y", "fill"))
```

# Color Info

This page shows the color info about colors.

```{r}

```

### Quantity and Weight

```{r include=FALSE}
# Fix the names of some of the countries in our data to match the country names 
# used by our map later on so that they'll be interpreted and displayed. 
data_cleaned <- data_cleaned %>%
  mutate(Country = fct_recode(Country, "Tanzania, United Republic Of" = "Tanzania"),
         Country = fct_recode(Country, "Papua New Guinea" = "The Independent State of Papua New Guinea"),
         Country = fct_recode(Country, "Costa Rica" = "The Republic of Costa Rica"),
         Country = fct_recode(Country, "El Salvador" = "The Republic of El Salvador"),
         Country = fct_recode(Country, "Cote d?Ivoire" = "The Republic of Cote d'ivoire"),
         Country = fct_recode(Country, "United States of America" = "United States"))

# Create new column in our data for continent. Use countrycode() to extract continents from country names.
data_cleaned$continent <- countrycode(sourcevar = data_cleaned$Country,
                              origin = "country.name",
                              destination = "continent")

# Reclassify countries that have been coded as 'Americas', by countrycode(), into 'North America' and 'South America'. 
south_america <- c('Brazil', 'Panama', 'Colombia', 'Costa Rica', 'Peru')

data_cleaned$continent[data_cleaned$Country %in% south_america] <- 'South America'
data_cleaned$continent[data_cleaned$continent=='Americas'] <- 'North America'
```

```{r}
color_list <- c("#ff7f0e", "#66a61e", "#d62728", "#1f78b4")

p <- ggplot(data_cleaned, aes(x = Number_of_bags, y = Bag_weight, color = Color)) +
  geom_point(alpha = 0.8) +
  scale_color_manual(values = color_list)  +
  theme_minimal()

p <- ggplotly(p, tooltip = "all", dynamicTicks = TRUE) %>%
  layout(
    title = list(text = "Quantity and Weight of Coffee by Color", font = list(size = 18, family = "Arial")),
    xaxis = list(title = "Number of Bags tested", titlefont = list(size = 12, family = "Arial"), tickfont = list(size = 10, family = "Arial")),
    yaxis = list(title = "Bag Weight tested", titlefont = list(size = 12, family = "Arial"), tickfont = list(size = 10, family = "Arial")),
    plot_bgcolor = "rgba(0, 0, 0, 0)",   # Set the plot background color to transparent
    paper_bgcolor = "rgba(0, 0, 0, 0)"   # Set the paper background color to transparent
  )

p
```

### Color distribution

```{r}
# Create a tibble of coffees by color
color_proportions <- data_cleaned %>%
  group_by(Color) %>%
  summarise(count = n()) %>%
  mutate(prop = count / sum(count))

# Custom colors for the pie chart
custom_colors <- c("#00FFFF", "#00CED1", "green", "grey")

# Create a pie chart using ggplot2
p <- ggplot(color_proportions, aes(x = "", y = prop, fill = Color, label = scales::percent(prop))) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  geom_text(aes(label = ifelse(prop > 0.03, scales::percent(prop), "")), position = position_stack(vjust = 0.5)) +
  coord_polar("y") +
  scale_fill_manual(values = custom_colors) +
  theme_void() +
  labs(
    title = "Worldwide Coffees by Color",
    subtitle = "2011 - 2018"
  ) +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(title = "Color"))

p

```

# Bar Chart {data-navmenu="Continent"}

### Number of Coffee Rating 5 by Continent - Bar Chart

This is showing the coffee rating of 5 that on each continent using Bar chart.

```{r}
library(ggplot2)
# install.packages("ggthemes")
library(ggthemes)
library(tidyverse)

# Calculate the number of coffee ratings equal to 5 for each continent
continent_tibble <- data_cleaned %>%
  group_by(continent) %>%
  summarize(number_of_ratings_5 = sum(Rating == 5, na.rm = TRUE)) %>%
  arrange(continent)

# Download continent map.
map_data <- map_data("world2")

ggplot(continent_tibble, aes(x = continent, y = number_of_ratings_5, fill = continent)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = RColorBrewer::brewer.pal(length(unique(continent_tibble$continent)), "Blues")) +
  labs(title = "Number of Coffee Rating 5 by Continent", subtitle = "2011 - 2018",
       x = "Continent", y = "Number of Ratings 5") +
  theme_minimal() +
  theme(legend.position = "none")
```

# Map Chart {data-navmenu="Continent"}

### Number of Coffee Rating 5 by Continent - Map Chart

This is showing the coffee rating of 5 that on each continent using a map.

```{r}
library(ggplot2)
library(ggthemes)
library(tidyverse)

# Calculate the number of coffee ratings equal to 5 for each continent
continent_tibble <- data_cleaned %>%
  group_by(continent) %>%
  summarize(number_of_ratings_5 = sum(Rating == 5, na.rm = TRUE)) %>%
  arrange(continent)

# Download continent map.
map_data <- map_data("world")


# Merge the map data and rating data by continent
merged_data <- merge(map_data, continent_tibble, by.x = "region", by.y = "continent", all.x = TRUE)

# Replace missing number_of_ratings_5 values with 0
merged_data$number_of_ratings_5[is.na(merged_data$number_of_ratings_5)] <- continent_tibble$number_of_ratings_5

# Create a map plot using ggplot
ggplot(merged_data, aes(x = long, y = lat, group = group, fill = number_of_ratings_5)) +
  geom_polygon(color = "black") +
  scale_fill_viridis_c(name = "Number of Ratings 5", 
                       breaks = continent_tibble$number_of_ratings_5,  # Set the breaks to the specified values
                       labels = continent_tibble$number_of_ratings_5,  # Set the labels to the specified values
                       guide = guide_legend(title = "Number of Ratings 5", reverse = TRUE)) +  # Customize the legend guide
  labs(title = "Number of Coffee Rating 5 by Continent", subtitle = "2011 - 2018") +
  theme_map()

```

# Map Interactive {data-navmenu="Continent"}

### Number of Coffee Rating 5 by Continent - Map Interactive

This is showing the coffee rating of 5 that on each continent using a interactive map.

```{r}
library(ggplot2)
library(ggthemes)
library(tidyverse)

# Calculate the number of coffee ratings equal to 5 for each continent
continent_tibble <- data_cleaned %>%
  group_by(continent) %>%
  summarize(number_of_ratings_5 = sum(Rating == 5, na.rm = TRUE)) %>%
  arrange(continent)

# Download continent map.
map_data <- map_data("world")


# Merge the map data and rating data by continent
merged_data <- merge(map_data, continent_tibble, by.x = "region", by.y = "continent", all.x = TRUE)

# Replace missing number_of_ratings_5 values with 0
merged_data$number_of_ratings_5[is.na(merged_data$number_of_ratings_5)] <- continent_tibble$number_of_ratings_5

ggplot(merged_data, aes(x = long, y = lat, group = group, fill = number_of_ratings_5)) +
  geom_polygon(color = "black") +
  scale_fill_gradientn(
    name = "Number of Ratings 5",
    colours = c("#f7fbff", "#08519c"),  # Customize the colors of the gradient
    breaks = continent_tibble$number_of_ratings_5,
    labels = continent_tibble$number_of_ratings_5,
    guide = guide_legend(title = "Number of Ratings 5", reverse = TRUE)
  ) +
  labs(title = "Number of Coffee Rating 5 by Continent", subtitle = "2011 - 2018") +
  theme_map() +
  theme(
    panel.background = element_blank(),  # Remove background color
    panel.border = element_blank(),  # Remove border around the map
    plot.title = element_text(size = 20),  # Increase title size
    plot.subtitle = element_text(size = 16),  # Increase subtitle size
    legend.title = element_text(size = 14),  # Increase legend title size
    legend.text = element_text(size = 12)  # Increase legend text size
  )
```

# Altitude Info

## Row 1 {data-height="300"}

### Year and Species

```{r,fig.width=8, fig.height=5}

data_grouped <- data_cleaned %>%
  group_by(Avg_Altitude) %>%
  summarize(Count = n())

ggplotly(
  ggplot(data_grouped, aes(x = Count, y = Avg_Altitude)) +
    geom_col(position = position_dodge()) +
    labs(title = "The Average Altitude of Coffee distribution",
         y = "Average altitude in different coffees",
         x = "Count") +
    theme(axis.text.x = element_text(hjust = 0, vjust = 1, size = 10, family = "Arial"),
          axis.text.y = element_text(size = 10, family = "Arial"),
          plot.title = element_text(size = 18, family = "Arial"),
          plot.subtitle = element_text(size = 13, family = "Arial"),
          axis.title.y = element_text(size = 12, family = "Arial"),
          legend.position = "bottom") +
    scale_x_continuous(limits = c(0, 23), breaks = seq(0, 23, by = 1))
)

```

## Row 2 {data-height="300"}

### Processing Method

```{r}

filtered_data <- data_cleaned %>%
  filter(Rating == 5)

# Create a ggplot object with increased transparency (alpha)
color_order <- c("#4CAF50", "#FF5722","#9C27B0")
scatter_plot_all <- ggplot(filtered_data, aes(x = Avg_Altitude, y = Total_Scores, color = Processing_method)) +
  geom_point(size=3,alpha = 0.7) +
  scale_color_manual(values = color_order) +
  labs(title = "Scatter Plot of Total_Scores vs Altitude and Processing Method")

# Convert ggplot to plotly
interactive_scatter_plot <- ggplotly(scatter_plot_all)

# Display the interactive plot
interactive_scatter_plot



```

# Worldwide Info

## Row

### Processing methods

```{r}
# processing
processing_proportions <- data_cleaned %>%
  group_by(Processing_method) %>%
  summarise(count = n()) %>%
  mutate(prop = count / sum(count))

# create
interactive_pie_chart <- plot_ly(processing_proportions, labels = ~Processing_method, values = ~prop, type = "pie",marker = list(colors = c("#4CAF50", "#FFC107", "#2196F3", "#FF5722", "#9C27B0"))) %>%
  layout(title = "Worldwide Coffees by Processing Methods",
         subtitle = "2011 - 2018",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

# show
interactive_pie_chart
```

# Country Scores {.storyboard}

```{r}


```

This page shows Average coffee scores by country.

### Average coffee scores by country - rainbow

```{r}
average_scores_by_country <- data_cleaned %>%
  group_by(Country) %>%
  summarize(Average_Total_Scores = mean(Total_Scores, na.rm = TRUE))

ggplot(average_scores_by_country, aes(x = Country, y = Average_Total_Scores, fill = Country)) +
  geom_bar(stat = "identity") +
  labs(title = "Average coffee scores by Country", subtitle = "2011 - 2018", 
       x = "Country", y = "Average Coffee Scores") +
  theme_minimal()
```

------------------------------------------------------------------------

Average coffee scores by country, rainbow theme

### Average coffee scores by country - rainbow, flip

```{r}
ggplot(average_scores_by_country, aes(x = reorder(Country, Average_Total_Scores), y = Average_Total_Scores, fill = Country)) +
  geom_bar(stat = "identity") +
  labs(title = "Average coffee scores by Country", subtitle = "2011 - 2018", 
       x = "Country", y = "Average Coffee Scores") +
  theme_minimal() +
  coord_flip()
```

------------------------------------------------------------------------

Average coffee scores by country, rainbow theme, showing each country name

### Average coffee scores by country - rainbow, flip, figure

```{r}
ggplot(average_scores_by_country, aes(x = reorder(Country, Average_Total_Scores), y = Average_Total_Scores, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.2f", Average_Total_Scores)), vjust = -0.5, size = 3.5) +
  labs(title = "Average coffee scores by Country", subtitle = "2011 - 2018", 
       x = "Country", y = "Average Coffee Scores") +
  theme_minimal() +
  coord_flip()
```

------------------------------------------------------------------------

Average coffee scores by country, rainbow theme, showing each country name and the exact figures.

### Average coffee scores by country - blues, interactive

```{r}
library(plotly)

average_scores_by_country <- average_scores_by_country %>%
  arrange(Average_Total_Scores)  # Reorder the data frame

# Create an interactive bar plot using plot_ly
plot_ly(average_scores_by_country, x = ~reorder(Country, Average_Total_Scores), y = ~Average_Total_Scores, type = "bar", 
        color = ~Country, colors = "Blues",
        text = ~paste("Country: ", Country, "<br>Average Coffee Scores: ", Average_Total_Scores)) %>%
  layout(title = "Average coffee scores by Country", xaxis = list(title = "Country"), yaxis = list(title = "Average Coffee Scores"))
```

------------------------------------------------------------------------

Average coffee scores by country, blue theme, showing information interactively.

### Average coffee scores by country - blues, interactive, flip

```{r}
average_scores_by_country <- average_scores_by_country %>%
  arrange(Average_Total_Scores)  # Reorder the data frame

# Create an interactive bar plot using plot_ly
plot_ly(average_scores_by_country, x = ~Average_Total_Scores, y = ~reorder(Country, Average_Total_Scores), type = "bar", 
        color = ~Country, colors = "Blues",
        text = ~paste("Country: ", Country, "<br>Average Coffee Scores: ", Average_Total_Scores)) %>%
  layout(title = "Average coffee scores by Country", xaxis = list(title = "Country"), yaxis = list(title = "Average Coffee Scores"))
```

------------------------------------------------------------------------

Average coffee scores by country, blue theme, showing information interactively and with fliped axis.

# Ratings Info

## Row 1

### The number of Ratings by Color

```{r}
library(ggplot2)
library(tidyverse)
rating_counts_by_species_color <- data_cleaned %>%
  group_by(Species, Color) %>%
  summarize(Count = n())

ggplot(rating_counts_by_species_color, aes(x = Species, y = Count, fill = Color)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "The number of Ratings by Color and Species", x = "Species", y = "") +
  theme(plot.title = element_text(size = 18, face = "bold", family = "Arial"),
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray", linetype = "dashed"))
  

```

### The number of Ratings by Species

```{r}
ggplot(rating_counts_by_species_color, aes(x = Color, y = Count, fill = Species)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Color", y = "") +
  theme(legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray", linetype = "dashed"))
```

## Row 2

### The number of Ratings by Color and Species

```{r}
library(ggplot2)
library(plotly)
library(dplyr)

rating_counts_by_species_color <- data_cleaned %>%
  group_by(Species, Color) %>%
  summarize(Count = n())

plot1 <- ggplot(rating_counts_by_species_color, aes(x = Species, y = Count, fill = Color)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "The number of Ratings by Color and Species", x = "Species", y = "") +
  theme(plot.title = element_text(size = 18, face = "bold", family = "Arial"),
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray", linetype = "dashed"))

plot2 <- ggplot(rating_counts_by_species_color, aes(x = Color, y = Count, fill = Species)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Color", y = "") +
  theme(legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray", linetype = "dashed"))

# Convert to plotly objects
plotly1 <- ggplotly(plot1)
plotly2 <- ggplotly(plot2)
plotly1
plotly2
```

Merged Plot
